\documentclass[11pt,a4paper]{article}
\usepackage[margin=1in]{geometry}
\usepackage{enumitem}
\usepackage{xcolor}
\usepackage{titlesec}
\usepackage{fontawesome5}
\usepackage[hidelinks]{hyperref}

\renewcommand{\familydefault}{\sfdefault}
\titleformat{\section}{\bfseries\Large\uppercase}{\thesection}{1em}{}
\setlist[itemize]{leftmargin=1.5em, itemsep=-4pt, topsep=1pt}

\begin{document}

% =====================
% Header
% =====================
\begin{center}
    {\LARGE \textbf{Le Xuan Huy}}\\[4pt]
    No. 139/1, Da Nam Street, Ward 3, District 8, Ho Chi Minh City\\[2pt]
    \faPhone*~0977221643 \quad 
    \faEnvelope~\href{mailto:lexuanhuy1994@gmail.com}{lexuanhuy1994@gmail.com} \quad 
    \faLink~\href{https://www.linkedin.com/in/huylx/}{https://www.linkedin.com/in/huylx/}
\end{center}

\vspace{0.5em}
\hrule
\vspace{0.5em}

% =====================
% SUMMARY
% =====================
\section*{SUMMARY}
Front-end developer with over 7 years of experience, including 4 years in full-stack roles. 
Skilled in developing modern, responsive, and high-performance web applications using the latest front-end frameworks. 
Focused on clean architecture, scalability, and delivering great user experiences.

\vspace{0.5em}
\hrule
\vspace{0.5em}

% =====================
% EDUCATION
% =====================
\section*{EDUCATION}
\noindent\textbf{Ho Chi Minh City Institute of Applied Science and Technology} \hfill \textbf{2012 -- 2015}\\
\textit{Major: Software Engineering}\\
\textit{GPA: 3.11 / 4.0}

\vspace{0.5em}
\hrule
\vspace{0.5em}

% =====================
% SKILLS
% =====================
\section*{SKILLS}
\begin{tabular}{@{}ll}
\textbf{Programming Languages} & - JavaScript, TypeScript \\
\textbf{Frameworks / Platforms} & - ReactJS, NextJS \\
                                & - TailwindCSS, Ant Design \\
\textbf{Databases}              & - MySQL, MongoDB \\
\textbf{Others}                 & - Experience with Git, Linux, Docker \\
\end{tabular}

\vspace{0.5em}
\hrule
\vspace{0.5em}

% =====================
% WORK EXPERIENCE
% =====================
\section*{WORK EXPERIENCE}

% --- GATLAS ---
\noindent\textbf{GATLAS CO., LTD} \hfill \textbf{June 2025 -- Present}\\
\textit{Front-end Developer}\\[2pt]
\textbf{Project:} Landing Page and MVP Product\\
\textbf{- Description:} Developed landing pages and MVP products integrated with AI.\\
\textbf{- Technologies:} ReactJS, AI Prompting\\
\textbf{- Responsibilities:}
\begin{itemize}
  \item Researched new AI tools to improve workflow efficiency.
  \item Wrote and fine-tuned prompts in Cursor to build MVP products.
\end{itemize}

\vspace{0.3em}
\hrule
\vspace{1.3em}

% --- WAREFLEX ---
\noindent\textbf{WAREFLEX SEA COMPANY LIMITED} \hfill \textbf{May 2023 -- June 2025}\\
\textit{Senior Front-end Developer / Technical Lead Front-end}\\[2pt]
\textbf{Project:} OMS, WMS, TMS, Marketplace\\
\textbf{- Description:} Built a management platform to connect customers with service providers.\\
\textbf{- Technologies:} ReactJS, NextJS\\
\textbf{- Responsibilities:}
\begin{itemize}
  \item Developed core UI components for the system.
  \item Coordinated with departments to gather and clarify requirements.
  \item Mentored and supported team members.
\end{itemize}

\vspace{0.3em}
\hrule
\vspace{1.3em}

% --- NEO PAYMENT ---
\noindent\textbf{Neo Payment JSC} \hfill \textbf{Apr 2022 -- Mar 2023}\\
\textit{Senior Front-end Developer}\\[2pt]
\textbf{Project:} Merchant Portal, NeoX Portal\\
\textbf{- Description:} Developed portal websites for merchants and internal operators.\\
\textbf{- Technologies:} ReactJS, Ant Design, UmiJS, DvaJS\\
\textbf{- Responsibilities:}
\begin{itemize}
  \item Researched UmiJS, DvaJS, and Ant Design to build reusable UI components.
  \item Wrote unit tests, optimized code, and resolved issues identified by SonarQube.
\end{itemize}

\vspace{0.3em}
\hrule
\vspace{1.3em}

% --- BOO TRADING ---
\noindent\textbf{BOO Trading JSC} \hfill \textbf{May 2020 -- Feb 2021}\\
\textit{Full-stack Developer}\\[2pt]
\textbf{Project:} BOO Marketplace Website\\
\textbf{- Description:} Developed an e-commerce platform for clothing and accessories.\\
\textbf{- Technologies:} PHP Laravel, VueJS, MySQL, Redis, RabbitMQ\\
\textbf{- Responsibilities:}
\begin{itemize}
  \item Built VueJS components for marketplace and admin websites.
  \item Developed APIs to synchronize data with a third-party ERP system.
  \item Used RabbitMQ for asynchronous operations (email notifications, ERP updates).
  \item Used Redis for caching to improve performance.
  \item Applied Jenkins for CI/CD build, deployment, and testing.
  \item Mentored junior team members.
\end{itemize}

\vspace{0.3em}
\hrule
\vspace{1.3em}

% --- AI PACIFIC ---
\noindent\textbf{AI Pacific} \hfill \textbf{Jan 2018 -- May 2020}\\
\textit{Full-stack Web Developer}\\[2pt]
\textbf{Project:} Human Resource Management System\\
\textbf{- Description:} Built internal applications for employee management.\\
\textbf{- Technologies:} ReactJS, PHP, MySQL, Redis\\
\textbf{- Responsibilities:}
\begin{itemize}
  \item Designed and implemented UI components for check-in/out, scheduling, and reporting.
  \item Developed real-time APIs using SailsJS.
  \item Maintained systems and supported data export requests.
\end{itemize}
\vspace{0.3em}
\textbf{Project:} Hospital Information System\\
\textbf{- Description:} Managed patient profiles, treatments, and billing.\\
\textbf{- Technologies:} ReactJS, PHP, MySQL, Redis\\
\textbf{- Responsibilities:}
\begin{itemize}
  \item Built UI components for payment and promotion modules.
  \item Used Redis for data caching.
  \item Maintained the system and supported data export for clients.
\end{itemize}

\vspace{0.3em}
\hrule
\vspace{1.3em}

% --- VNETWORK ---
\noindent\textbf{VNETWORK JSC} \hfill \textbf{May 2015 -- Dec 2017}\\
\textit{Junior Web Developer}\\[2pt]
\textbf{Project:} Company Websites (vnetwork.vn, vncdn.vn)\\
\textbf{- Description:} Upgraded and maintained company websites.\\
\textbf{- Technologies:} PHP, JQuery, Twitter Bootstrap\\
\textbf{- Responsibilities:}
\begin{itemize}
  \item Converted PSD files to HTML and implemented new UIs.
  \item Developed and maintained internal system features.
\end{itemize}
\vspace{0.3em}
\textbf{Project:} Customer Websites\\
\textbf{- Description:} Developed custom WordPress websites for clients.\\
\textbf{- Technologies:} WordPress\\
\textbf{- Responsibilities:}
\begin{itemize}
  \item Converted PSD designs to HTML and integrated into WordPress.
  \item Customized WordPress features based on client requirements.
\end{itemize}

\end{document}
